Predicted cardiovascular risk and blood pressure for Americans with diabetes, chronic kidney disease, and \u226565 years of age

### 2020-09-24 doc/ACCAHA_BP_groups.Rmd
first draft sent to co-authors

abbrev_key <- c(
  `ACC/AHA` = 'American College of Cardiology and the American Heart Association',
  CI = 'confidence interval',
  BP = 'blood pressure',
  NHANES = 'National Health and Nutrition Examination Survey',
  SBP = 'systolic BP',
  DBP = 'diastolic BP',
  CKD = 'chronic kidney disease',
  CVD = 'cardiovascular disease',
  ASCVD = 'atherosclerotic CVD',
  ACR = 'albumin-to-creatinine ratio',
  HbA1c = 'glycated hemoglobin',
  eGFR = 'estimated glomerular filtration rate'
) %>% 
  enframe(name = 'acronym', value = 'phrase') %>% 
  mutate(counter = 0)

@@

@@

@@

@@

The 2017 `r ACC_AHA()` guideline recommends computing 10-year predicted risk for `r ASCVD()` in all adults with hypertension to establish a `r BP()` threshold for treatment.[@whelton20182017] However, it has been suggested that the vast majority of adults with diabetes, CKD, or ≥ 65 years of age are likely to have a 10-year predicted risk for `r ASCVD()` ≥ 10%. The purpose of the current analysis was to estimate the proportion of US adults with diabetes, `r CKD()`, or ≥ 65 years of age that have high `r ASCVD()` risk (i.e., a 10-year predicted risk for `r ASCVD()` ≥ 10% or prevalent `r CVD()`).  A secondary objective was to estimate the proportion of adults with stage 1 hypertension and diabetes, `r CKD()`, or age ≥ 65 years who have high `r ASCVD()` risk, as the 2017 `r ACC_AHA()` `r BP()` guideline recommends initiation of antihypertensive medication for these individuals. To accomplish these goals, we analyzed data from `r english(length(exams))` cycles of the US `r NHANES()`.

@@

Data were collected during an in-home interview and a study visit completed at a mobile examination center. Standardized questionnaires were used to assess participants’ age, sex, race/ethnicity, smoking habits, medical history and use of antihypertensive medication, oral glucose lowering medication and insulin. Medical history included questions about whether the participant had been told by a doctor or other health professional that they have had a heart attack, coronary heart disease stroke, or heart failure. Blood and urine samples were collected during the medical examination. Of relevance to the current analysis, serum creatinine, serum glucose and `r HB_A1C()` were measured. Diabetes was defined by fasting serum glucose ≥ `r gluc_cutpoint_fasted` mg/dL, non-fasting glucose ≥ `r gluc_cutpoint_fed` mg/dL, `r HB_A1C()` ≥ `r hba1c_cutpoint`%, or self-reported use of insulin or oral glucose lowering medication. `r capitalize(E_GFR())` was calculated using the Chronic Kidney Disease Epidemiology Collaboration equation.[@levey2009new] Urinary albumin and creatinine levels were measured and used to calculate the `r ACR()`. `r CKD()` was defined by an `r E_GFR()` < `r egfr_cutpoint` ml/min/1.73m^2^ or an `r ACR()` ≥ `r acr_cutpoint` mg/dL. Predicted 10-year risk for `r ASCVD()` was calculated using the Pooled Cohort risk equations for participants without prevalent `r CVD()`.[@goff20142013] High `r ASCVD()` risk was defined as prevalent `r CVD()` or a 10-year predicted `r ASCVD()` risk ≥ 10%.

@@

`r NHANES()` sampling weights, which were calculated as the inverse probability of being selected for the survey, were used in all calculations to obtain nationally representative estimates of the non-institutionalized US population. The survey design of `r NHANES()` was also taken into account in all calculations. P-values were two-sided. Data analysis was conducted using `r R_string_fancy` along with a collection of open-source software packages.[@cite_R; @cite_drake; @cite_tidyverse; @cite_table.glue] The first author's GitHub repository (< _Link not yet active so we won't be scooped_ >) provides code to reproduce the current manuscript.

@@

Among US adults aged 40 to 79 years in `r min(exams)`-`r max(exams)+1`, the estimated prevalence (95% `r CI(left_mark = '[', right_mark = ']')`) of diabetes and `r CKD()` was `r inline$prevDiabetesOverall` and `r inline$prevCkdOverall`, respectively, `r inline$prevAge65Overall` were estimated to have ≥ 65 years of age, and `r inline$prevAnyOverall` had at least one of these conditions (`r refer_to('tab_characteristics')`). An estimated `r inline$prevS1hOverall` of US adults 40 to 79 years of age had stage 1 hypertension (`r refer_to('tab_bpdist')`). Among those with diabetes, CKD, age ≥ 65 years, and any of these three conditions, the estimated prevalence (95% `r CI()`) of stage 1 hypertension was `r inline$prevS1hDiabetes`, `r inline$prevS1hCkd`, `r inline$prevS1hAge65`, `r inline$prevS1hAny`, respectively. Characteristics of US adults 40 to 79 years of age with stage 1 hypertension, overall and for subgroups defined by diabetes, `r CKD()` and age ≥ 65 years, are presented in Table S1.

@@

Among US adults aged 40 to 79 years without prevalent `r CVD()`, the estimated median (25^th^, 75^th^ percentiles) 10-year predicted risk for `r ASCVD()` was `r inline$medianPcrOverall` overall and `r inline$medianPcrDiabetes`, `r inline$medianPcrCkd`, `r inline$medianPcrAge65`, `r inline$medianPcrAny` among those with diabetes, CKD, age ≥ 65 years, and any of these three conditions, respectively (`r refer_to('tab_risk_overall')`; top panel). Among those with stage 1 hypertension, the estimated median (25^th^, 75^th^ percentiles) 10-year predicted risk for `r ASCVD()` was `r inline$medianPcrS1hOverall` overall and `r inline$medianPcrS1hDiabetes`, `r inline$medianPcrS1hCkd`, `r inline$medianPcrS1hAge65`, `r inline$medianPcrS1hAny` among those with diabetes, CKD, age ≥ 65 years, and any of these three conditions, respectively.

@@

Among US adults aged 40 to 79 years, the estimated percentage (95% `r CI()`) at high ASCVD risk was `r inline$prevHighRiskOverall` overall and `r inline$prevHighRiskDiabetes`, `r inline$prevHighRiskCkd`, `r inline$prevHighRiskAge65`, and `r inline$prevHighRiskAny` for those with diabetes, `r CKD()`, age ≥ 65 years, or any of these three conditions, respectively (`r refer_to('tab_risk_overall')`; bottom panel). Among those with stage 1 hypertension, an estimated `r inline$prevHighRiskS1hOverall` had high `r ASCVD()` risk overall and `r inline$prevHighRiskS1hDiabetes`, `r inline$prevHighRiskS1hCkd`, `r inline$prevHighRiskS1hAge65`, and `r inline$prevHighRiskS1hAny` of those with diabetes, `r CKD()`, age ≥ 65 years, or any of these three conditions had high `r ASCVD()` risk, respectively.

@@

Among US adults aged 40 to 79 years who were not at high risk for `r ASCVD()`, an estimated `r inline$propLowRiskOverall` had 10-year predicted `r ASCVD()` risk < 5% (`r refer_to('fig_hist_ovrl')`). Among those not at high risk for `r ASCVD()` with diabetes, `r CKD()` age ≥ 65 years, and any of these three conditions, an estimated `r inline$propLowRiskDiabetes`, `r inline$propLowRiskCkd`, `r inline$propLowRiskAge65`, and `r inline$propLowRiskAny` had a 10-year predicted `r ASCVD()` risk < 5%, respectively. Among those not at high risk for `r ASCVD()` and with stage 1 hypertension, an estimated `r inline$propLowRiskS1hOverall` overall and  `r inline$propLowRiskS1hDiabetes`, `r inline$propLowRiskS1hCkd`, and `r inline$propLowRiskS1hAge65` of those with diabetes, CKD, and ≥ 65 years of age had a 10-year predicted `r ASCVD()` risk < 5%, respectively (`r refer_to('fig_hist_stg1')`).

@@

In the current study, a majority of US adults aged 40 to 79 years with diabetes, `r CKD()`, age ≥ 65 years, and any of these three conditions had a high risk for `r ASCVD()`, defined by a 10-year predicted `r ASCVD()` risk ≥ 10% or prevalent `r CVD()`. Among those with stage 1 hypertension and ≥ 65 years of age, a substantial proportion were at high `r ASCVD()` risk. However, a substantial proportion of US adults with stage 1 hypertension and diabetes or CKD did not have high `r ASCVD()` risk. Among US adults with diabetes or CKD who were not at high `r ASCVD()` risk, approximately half had a 10-year predicted `r ASCVD()` risk < 5%. In contrast, over 80% of US adults aged ≥ 65 years not at high `r ASCVD()` risk had 10-year predicted risk for `r ASCVD()` between 5% and 10%. The probability of having high `r ASCVD()` risk was age-dependent with over 50% of those with diabetes, `r CKD()`, and with neither of these conditions expected to have high `r ASCVD()` risk at ≥ `r inline$ageHighRiskOvrlDiabetes`, ≥ `r inline$ageHighRiskOvrlCkd`, and ≥ `r inline$ageHighRiskOvrlNoComorb` years of age, respectively.

@@

The current study estimates that roughly 33% of US adults aged 40 to 79 years take antihypertensive medication, including half of those with diabetes, CKD, or ≥ 65 years of age. Among those with diabetes, `r CKD()`, or age ≥ 65 years, only about 10% had stage 1 hypertension. The 2017 `r ACC_AHA()` `r BP()` guideline recommends all of these adults initiate antihypertensive medication and also recommends computing 10-year predicted `r ASCVD()` risk to establish the `r BP()` threshold for treatment.[@whelton20182017] The heterogeneous distribution of 10-year predicted `r ASCVD()` among those with stage 1 hypertension and diabetes, `r CKD()`, or age ≥ 65 years emphasizes the importance of these two recommendations from the guideline. Prior studies have shown the 2017 `r ACC_AHA()` `r BP()` guideline directs antihypertensive medication to those most likely to receive the largest risk reduction benefit,[@colantonio20182017; @jaeger2019cardiovascular] and computing 10-year predicted risk for `r ASCVD()` can both inform patients and facilitate patient provider discussions on a `r BP()` threshold for treatment.

@@

Previous studies have shown that the use of predicted `r ASCVD()` risk in addition to `r BP()`, as recommended by the 2017 `r ACC_AHA()` `r BP()` guideline, can direct antihypertensive medication to adults likely to receive the largest risk reduction benefit with treatment.[@colantonio20182017] In an analysis of the Reasons for Geographic and Racial Differences in Stroke study, those with stage 1 hypertension recommended versus not recommended to initiate antihypertensive medication by the 2017 `r ACC_AHA()` `r BP()` guideline were roughly 6 times more likely to experience a `r CVD()` event over 8 years of follow-up. Although a substantial proportion of US adults with stage 1 hypertension and diabetes, `r CKD()`, or ≥ 65 years of age did not have a high `r ASCVD()` risk in the current study, they were more likely to have high `r ASCVD()` risk compared to the overall US population with stage 1 hypertension, and may therefore still benefit from initiating antihypertensive medication.

@@

In conclusion, a majority of US adults aged 40 to 79 years with diabetes, `r CKD()` or ≥ 65 years of age had 10-year predicted risk for `r ASCVD()` ≥ 10%. However, a lower percentage of those with stage 1 hypertension and diabetes, `r CKD()` or ≥ 65 years of age had 10-year predicted risk for `r ASCVD()` ≥ 10%. While most older US adults with diabetes or `r CKD()` had high `r ASCVD()` risk, a substantial proportion of younger adults with diabetes or `r CKD()` did not. Results from the current study support computing 10-year predicted `r ASCVD()` risk for all adults with hypertension, as recommended by the 2017 `r ACC_AHA()` `r BP()` guideline.

>>>>

abbrev_key <- c(
  CVD = 'cardiovascular disease',
  ASCVD = 'atherosclerotic CVD',
  `ACC/AHA` = 'American College of Cardiology and the American Heart Association',
  BP = 'blood pressure',
  SBP = 'systolic BP',
  DBP = 'diastolic BP',
  CKD = 'chronic kidney disease',
  NHANES = 'National Health and Nutrition Examination Survey',
  CI = 'confidence interval',
  ACR = 'albumin-to-creatinine ratio',
  HbA1c = 'glycated hemoglobin',
  eGFR = 'estimated glomerular filtration rate'
) %>% 
  enframe(name = 'acronym', value = 'phrase') %>% 
  mutate(counter = 0)

@@

Total word count: __FILL THIS IN__

@@

__Funding:__ Information on grants, contracts, and other forms of financial support. _Please add your data if needed_

__Disclosures:__ State each author's disclosures (or lack thereof). This must include the full disclosure of any relationship with industry. _Please add your statement below_

BCJ has nothing to disclose.

__Address for correspondence:__
Byron C. Jaeger
University of Alabama at Birmingham
327M Ryals Public Health Building
1665 University Blvd
Birmingham, Alabama 35294-0022

__Acknowledgments:__ to be drafted in next version.

@@

# ABSTRACT

_Note: Maximum word count is 250_

__Background:__ The 2017 American College of Cardiology/American Heart Association blood pressure (BP) guideline recommends predicting 10-year atherosclerotic cardiovascular disease (ASCVD) risk for adults with hypertension to establish a BP treatment threshold. However, it has been suggested that most adults with diabetes, chronic kidney disease (CKD), and age≥65 years have 10-year predicted ASCVD risk≥10%.

__Objectives:__ In subgroups of US adults defined by diabetes, CKD, and age≥65 years, determine whether the majority have high ASCVD risk (i.e., 10-year predicted ASCVD risk≥10% or prevalent CVD), and estimate age-adjusted probability of high ASCVD risk.

__Methods:__ Adults aged 40-79 years from the 2013-2018 National Health and Nutrition Examination Survey were included. Age-adjusted probability of high ASCVD risk was estimated using logistic regression. Analyses were conducted overall and among those with stage 1 hypertension.

__Results:__ Among US adults overall (with stage 1 hypertension), an estimated 72.5% (55.0%), 64.5% (36.7%), 83.9% (72.6%), and 69.1% (54.4%) had high ASCVD risk in subgroups with diabetes, CKD, age≥65 years, and any of these conditions, respectively. Probability of high ASCVD risk exceeded 50% in subgroups with diabetes, CKD, and neither diabetes nor CKD at age 54 (55), 59 (65), and 65 (65) years, respectively.

__Conclusions:__ While the majority of US adults with diabetes, CKD, or age≥65 years had high ASCVD risk, many with stage 1 hypertension did not. Predicted 10-year ASCVD risk is heterogeneous among adults with stage 1 hypertension and diabetes or CKD, and should be computed for all adults with hypertension to establish appropriate BP treatment thresholds.

__Key words__: Atherosclerotic cardiovascular disease, blood pressure, diabetes, chronic kidney disease, risk prediction

# ABBREVIATIONS

```{r, results='asis'}

abbrev_key %>% 
  slice(1:max_abbrevs) %>%
  select(-counter) %>% 
  mutate(phrase = str_replace(phrase, 'BP', 'blood pressure'),
         phrase = str_replace(phrase, 'CVD', 'cardiovascular disease')) %>% 
  glue_data("{acronym} = {phrase}") %>% 
  glue_collapse(sep = '\n\n\n')

# CONDENSED ABSTRACT

_Note: No more than 100 words, stressing clinical implications_

The 2017 American College of Cardiology/American Heart Association blood pressure (BP) guideline recommends predicting 10-year atherosclerotic cardiovascular disease (ASCVD) risk for adults with hypertension to establish BP treatment thresholds. However, it has been suggested that most adults with diabetes, chronic kidney disease, and age≥65 years have 10-year predicted ASCVD risk≥10%. Nationally representative data show many US adults with stage 1 hypertension and diabetes or chronic kidney disease do not have 10-year predicted ASCVD risk≥10% or prevalent CVD. Predicted 10-year ASCVD risk is heterogeneous among adults with stage 1 hypertension and should be computed to establish appropriate BP treatment thresholds.

# Central Illustration:

_To be determined_

# Clinical Perspectives:

_To be drafted in next version_

# INTRODUCTION

@@

The 2017 `r ACC_AHA()` guideline recommends computing 10-year predicted risk for `r ASCVD()` in all adults with hypertension to establish a `r BP()` threshold for treatment.[@whelton20182017] However, it has been suggested that the vast majority of adults with diabetes, CKD, or ≥ 65 years of age are likely to have a 10-year predicted risk for `r ASCVD()` ≥ 10%. The purpose of the current analysis was to estimate the proportion of US adults with diabetes, `r CKD()`, or ≥ 65 years of age that have high `r ASCVD()` risk (i.e., a 10-year predicted risk for `r ASCVD()` ≥ 10% or prevalent `r CVD()`) and estimate the age-adjusted probability of high `r ASCVD()` risk in these groups.  Analyses were replicated among adults with stage 1 hypertension since the 2017 `r ACC_AHA()` `r BP()` guideline recommends initiation of antihypertensive medication for adults with stage 1 hypertension and diabetes, `r CKD()`, or age ≥ 65 years, and initiation may involve determining a BP treatment threshold. To accomplish these goals, we analyzed data from `r english(length(exams))` cycles of the US `r NHANES()`.

@@

Data were collected during an in-home interview and a study visit completed at a mobile examination center. Standardized questionnaires were used to assess participants’ age, sex, race/ethnicity, smoking habits, medical history and use of antihypertensive medication, oral glucose lowering medication and insulin. Medical history included questions about whether the participant had been told by a doctor or other health professional that they have had a heart attack, coronary heart disease stroke, or heart failure. Prevalent `r CVD()` was defined as answering 'yes' to at least one of these questions.

Blood and urine samples were collected during the medical examination. Of relevance to the current analysis, serum creatinine, serum glucose and `r HB_A1C()` were measured. Diabetes was defined by fasting serum glucose ≥ `r gluc_cutpoint_fasted` mg/dL, non-fasting glucose ≥ `r gluc_cutpoint_fed` mg/dL, `r HB_A1C()` ≥ `r hba1c_cutpoint`%, or self-reported use of insulin or oral glucose lowering medication. `r capitalize(E_GFR())` was calculated using the Chronic Kidney Disease Epidemiology Collaboration equation.[@levey2009new; @cite_nephro] Urinary albumin and creatinine levels were measured and used to calculate the `r ACR()`. `r CKD()` was defined by an `r E_GFR()` < `r egfr_cutpoint` ml/min/1.73m^2^ or an `r ACR()` ≥ `r acr_cutpoint` mg/dL. Predicted 10-year risk for `r ASCVD()` was calculated using the Pooled Cohort risk equations for participants without prevalent `r CVD()`.[@goff20142013] High `r ASCVD()` risk was defined as prevalent `r CVD()` or a 10-year predicted `r ASCVD()` risk ≥ 10%.

@@

`r NHANES()` sampling weights, which were calculated as the inverse probability of being selected for the survey, were used in all calculations to obtain nationally representative estimates of the non-institutionalized US population. The survey design of `r NHANES()` was also taken into account in all calculations. P-values were two-sided. Data analysis was conducted using `r R_string_fancy` along with a collection of open-source software packages.[@cite_R; @cite_drake; @cite_tidyverse; @cite_table.glue] The first author's GitHub repository (< _Link not yet active so we won't be scooped_ >) provides code to reproduce the current study, allowing for different initial parameters.

@@

Among US adults aged 40 to 79 years in `r min(exams)`-`r max(exams)+1`, the estimated prevalence (95% `r CI(left_mark = '[', right_mark = ']')`) of diabetes and `r CKD()` was `r inline$prevDiabetesOverall` and `r inline$prevCkdOverall`, respectively, `r inline$prevAge65Overall` were estimated to have ≥ 65 years of age, and `r inline$prevAnyOverall` had at least one of these conditions (`r refer_to('tab_characteristics')`). The estimated prevalence (95% `r CI()`) of stage 1 hypertension was `r inline$prevS1hOverall` overall and `r inline$prevS1hDiabetes`, `r inline$prevS1hCkd`, `r inline$prevS1hAge65`, and `r inline$prevS1hAny` among those with diabetes, CKD, age ≥ 65 years, and at least one of these conditions, respectively (`r refer_to('tab_bpdist')`). Characteristics of US adults 40 to 79 years of age with stage 1 hypertension, overall and for subgroups defined by diabetes, `r CKD()` and age ≥ 65 years, are presented in Table S1.

@@

Among US adults aged 40 to 79 years without prevalent `r CVD()`, the estimated median (25^th^, 75^th^ percentiles) 10-year predicted risk for `r ASCVD()` was `r inline$medianPcrOverall` overall and `r inline$medianPcrDiabetes`, `r inline$medianPcrCkd`, `r inline$medianPcrAge65`, `r inline$medianPcrAny` among those with diabetes, CKD, age ≥ 65 years, and any of these conditions, respectively (`r refer_to('tab_risk_overall')`; top panel). Among those with stage 1 hypertension, the estimated median (25^th^, 75^th^ percentiles) 10-year predicted risk for `r ASCVD()` was `r inline$medianPcrS1hOverall` overall and `r inline$medianPcrS1hDiabetes`, `r inline$medianPcrS1hCkd`, `r inline$medianPcrS1hAge65`, `r inline$medianPcrS1hAny` for those with diabetes, CKD, age ≥ 65 years, and any of these conditions, respectively.

@@

Among US adults aged 40 to 79 years, the estimated percentage (95% `r CI()`) at high ASCVD risk was `r inline$prevHighRiskOverall` overall and `r inline$prevHighRiskDiabetes`, `r inline$prevHighRiskCkd`, `r inline$prevHighRiskAge65`, and `r inline$prevHighRiskAny` for those with diabetes, `r CKD()`, age ≥ 65 years, or any of these conditions, respectively (`r refer_to('tab_risk_overall')`; bottom panel). Among those with stage 1 hypertension, the estimated percentage (95% `r CI()`) at high `r ASCVD()` risk was `r inline$prevHighRiskS1hOverall` overall and `r inline$prevHighRiskS1hDiabetes`, `r inline$prevHighRiskS1hCkd`, `r inline$prevHighRiskS1hAge65`, and `r inline$prevHighRiskS1hAny` for those with diabetes, `r CKD()`, age ≥ 65 years, or any of these conditions, respectively.

@@

Among US adults aged 40 to 79 years who were not at high risk for `r ASCVD()`, an estimated `r inline$propLowRiskOverall` had 10-year predicted `r ASCVD()` risk < 5% (`r refer_to('fig_hist_ovrl')`). Among those not at high risk for `r ASCVD()` with diabetes, `r CKD()`, age ≥ 65 years, and any of these conditions, an estimated `r inline$propLowRiskDiabetes`, `r inline$propLowRiskCkd`, `r inline$propLowRiskAge65`, and `r inline$propLowRiskAny` had a 10-year predicted `r ASCVD()` risk < 5%, respectively. Among those not at high risk for `r ASCVD()` and with stage 1 hypertension, an estimated `r inline$propLowRiskS1hOverall` overall and  `r inline$propLowRiskS1hDiabetes`, `r inline$propLowRiskS1hCkd`, and `r inline$propLowRiskS1hAge65` of those with diabetes, CKD, and ≥ 65 years of age had a 10-year predicted `r ASCVD()` risk < 5%, respectively (`r refer_to('fig_hist_stg1')`).

@@

In the current study, a majority of US adults aged 40 to 79 years with diabetes, `r CKD()`, age ≥ 65 years, and any of these conditions had a high risk for `r ASCVD()`, defined by a 10-year predicted `r ASCVD()` risk ≥ 10% or prevalent `r CVD()`. Among those with stage 1 hypertension and ≥ 65 years of age, a substantial proportion were at high `r ASCVD()` risk. However, a substantial proportion of US adults with stage 1 hypertension and diabetes or CKD did not have high `r ASCVD()` risk. Among US adults with diabetes or CKD who were not at high `r ASCVD()` risk, approximately half had a 10-year predicted `r ASCVD()` risk < 5%. In contrast, over 80% of US adults aged ≥ 65 years not at high `r ASCVD()` risk had 10-year predicted risk for `r ASCVD()` between 5% and 10%. The probability of having high `r ASCVD()` risk was age-dependent with over 50% of those with diabetes, `r CKD()`, and with neither of these conditions expected to have high `r ASCVD()` risk at ≥ `r inline$ageHighRiskOvrlDiabetes`, ≥ `r inline$ageHighRiskOvrlCkd`, and ≥ `r inline$ageHighRiskOvrlNoComorb` years of age, respectively.

@@

The current study estimates that roughly one third of US adults aged 40 to 79 years take antihypertensive medication, including one half of those with diabetes, CKD, or ≥ 65 years of age. Among those with diabetes, `r CKD()`, or age ≥ 65 years, about 10% had stage 1 hypertension. The heterogeneous distribution of 10-year predicted `r ASCVD()` among those with stage 1 hypertension and diabetes, `r CKD()`, or age ≥ 65 years emphasizes the importance of the 2017 `r ACC_AHA()` `r BP()` guideline's recommendation to compute 10-year predicted `r ASCVD()` risk for all adults with hypertension.[@whelton20182017] Computing 10-year predicted `r ASCVD()` risk can inform patients recommended to initiate antihypertensive medication and later facilitate patient provider discussions on a `r BP()` threshold for treatment.

@@

Previous studies have shown that the use of predicted `r ASCVD()` risk in addition to `r BP()`, as recommended by the 2017 `r ACC_AHA()` `r BP()` guideline, can direct antihypertensive medication to adults likely to receive the largest risk reduction benefit with treatment.[@colantonio20182017; @jaeger2019cardiovascular] In an analysis of the Reasons for Geographic and Racial Differences in Stroke study, those with stage 1 hypertension recommended versus not recommended to initiate antihypertensive medication by the 2017 `r ACC_AHA()` `r BP()` guideline were roughly 6 times more likely to experience a `r CVD()` event over 8 years of follow-up. Although a substantial proportion of US adults with stage 1 hypertension and diabetes, `r CKD()`, or ≥ 65 years of age did not have a high `r ASCVD()` risk in the current study, they were more likely to have high `r ASCVD()` risk compared to the overall US population with stage 1 hypertension, and may therefore still benefit from initiating antihypertensive medication.

@@

# CONCLUSIONS

While the majority of US adults with diabetes, `r CKD()`, or age≥65 years had high `r ASCVD()` risk, many with stage 1 hypertension did not. Most older US adults with diabetes or `r CKD()` had high `r ASCVD()` risk, but a substantial proportion of younger adults with diabetes or `r CKD()` did not. Results from the current study support computing 10-year predicted `r ASCVD()` risk for all adults with hypertension, as recommended by the 2017 `r ACC_AHA()` `r BP()` guideline.
